HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-03-25 LaTeX/ms.tex
Minor edits

An excess of sources with small separations from each other could be an
indication of interacting or merging systems.  However, it is also possible
that the sources are merely unrelated galaxies that appear blended due to
projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
to answer this question definitely, but is not currently available.  Instead,
to investigate these possibilities further, we make use of mock catalogs of
DSFGs that are based on numerical simulations and presented by \citet{HB13}.
We summarize the methodology used to generate $dN/dA$ values from the mock
catalogs here and refer the reader to \citet{HB13} for full details.

@@

We explore a variety of intrinsic luminosity functions that are described by
either a single Schechter function or a broken-power law.  These luminosity
functions are selected to represent the range of observed instrinsic luminosity
functions for DSFGs, which are shown in the left panel of
Figure~\ref{fig:lensstats} and are drawn from the ALESS survey
\citep{Karim:2013lr} and from interferometric follow-up of the first AzTEC
survey in COSMOS \citep{Scott:2008qy} using the SMA \citep{Younger:2007fk,
Younger:2009lr} and PdBI (Miettinen et al., in prep.).  Interferometric
follow-up data in COSMOS \citep{Smolcic:2012zl} and GOODS-N
\citep{Barger:2012yg} are published, but unknown completeness corrections in the
single-dish surveys on which these follow-up datasets are based precludes their
use here.

@@

In Table~\ref{tab:models}, we provide information for three models tested in
this paper: the steepest plausible Schechter function; the \citet{Karim:2013lr}
broken power-law; and a broken power-law with a brighter break point ($S_\ast =
15\,$mJy) than used in \citet{Karim:2013lr}.

@@

The middle panel of Figure~\ref{fig:lensstats} shows a direct comparison of the
measured $\mu_{870}$ values as a function of apparent $S_{870}$ for the {\it
Herschel}-ALMA and {\it Herschel}-SMA samples.  We also show a running average
of the combined sample (considering only $\mu_{870} > 1.1$ objects, since this
is the level at which magnification effects become as significant as absolute
calibration uncertainties) to serve as a direct comparison to our theoretical
models.  We compute this by interpolating the observed $\mu_{870}$ and
$S_{870}$ onto a fine grid using the {\sc Scipy} {\sc griddata} package and
then smoothing the resulting grid using a Gaussian filter (specifically, the
Scipy {\sc gaussian\_filter} package).  Also shown in this diagram are model
predictions for the average magnification as a function of $S_{870}$,
$\langle\mu_{870}\rangle$, assuming the three intrinsic luminosity functions
for DSFGs described in Table~\ref{tab:models}.

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=0.335\textwidth]{../Figures/DifferentialNumberCounts.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/s870_mu.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/Pmu_S870.pdf}

\caption{ {\it Left}: Observed luminosity functions from interferometer
follow-up of mm sources in COSMOS \citep[black circles;][Miettinen et al., in
prep.]{Younger:2007fk, Younger:2009lr} and from ALESS \citep[pink
diamonds;][]{Karim:2013lr}.  In comparison, the magneta, purple, and blue lines
show three models for the intrinsic luminosity functions of DSFGs. {\it Middle}:
Magnification factors at 870$\,\mu$m as a function of apparent $S_{870}$ for
every source in our ALMA (green squares) and SMA (red circles) samples.  The
black line represents a running average of the magnification measurements when
sources with $\mu_{870} > 1.1$ are considered.  Colored lines show our model
predictions $<\mu_{870}>$ for $\mu_{870} > 1.1$ sources for the three intrinsic
luminosity functions shown on the left.  All three luminosity functions are
broadly consistent with the observed magnification factors.  {\it Right}:
Probability that a source with a given $S_{870}$ experiences $\mu_{870} > 1.1$
(solid lines) and $\mu_{870} > 2.0$ (dashed lines).  The black lines show the
running average from the SMA and ALMA data.  Colored lines are the same as in
the middle and left panels.  The Schechter function predicts too many unlensed
or weakly lensed sources with intrinsic flux densities of $S_{870}^\prime \sim
50\,$mJy.  Our choices for the broken power-law luminosity functions roughly
bracket the running average from the data.} \label{fig:lensstats}

@@

At low apparent flux densities ($S_{870} < 10\,$mJy), all three models are
broadly consistent with each other, as well as with the running average of the
data, considering the dispersion in the model predictions for $\mu_{870}$ at a
given $S_{870}$ are $\sigma_\mu \approx 1-2$ in this regime.

The regime between the low and high apparent flux density limits ($10\,$mJy$ <
S_{870} < 70\,$mJy) is where the three model predictions show the largest
difference in $\langle\mu_{870}\rangle$.  The steep rise in the running average in this
area is best reproduced by the model with the steep broken power-law luminosity
function.  However, this model has a difficult time accounting for the
low-$\mu_{870}$, high-$S_{870}$ population that comprises about one-third of
the sources in this regime.  Because the dispersion in the model magnification
factors rises smoothly from $\sigma_\mu \approx 2$ to $\sigma_\mu \approx 8$
over this regime, this difference is significant.  The steep Schechter function
does a better job of reproducing the low-magnification sources, but it
under-predicts the running average over much of the range in $S_{870}$.
Furthermore, there are a number of high-$\mu_{870}$, $S_{870} \approx
10-20\,$mJy sources that are poorly accounted for by the steep Schechter
function.  The broken power-law luminosity function advocated in
\citet{Karim:2013lr} provides an intermediate result between the steep
Schechter function and steep broken power-law and therefore shares some of the
strengths and weaknesses of both.

At high apparent flux densities ($S_{870} > 70\,$mJy), all of the models
over-predict the running average of the magnification.  One plausible
explanation for this difference is a limitation in the spatial resolution of
the observations.  In both the {\it Herschel}-ALMA and {\it Herschel}-SMA
samples, the spatial resolution is $\approx 0\farcs5$.  This is nearly always
sufficient to resolve the images of the lensed galaxy, but it is not always
sufficient to resolve the images themselves.  Therefore, it may be the case
that the lens models over-predict the intrinsic sizes of the lensed galaxies
and hence under-predict the magnification factors.  For example, the half-light
sizes of unlensed DSFGs have been found recently to be $\approx 0.8 \,$kpc
\citep{Ikarashi:2014nr} and $\approx1.2\,$kpc \citep{Simpson:2015ty}.  In
contrast, we reported a median half-light radius of $1.53\,$kpc in
\citet{Bussmann:2013lr}.  If this difference is significant, it may also affect
the intermediate $S_{870}$ regime.  A thorough investigation of this
possibility is deferred to future work.

One way to deal with this potential limitation in the data is to simplify the
quantity of interest.  In particular, we next consider the probability of a
given source experiencing a magnification above some threshold value, $\mu_{\rm
min}$.  As discussed previously, we expect our ALMA and SMA measurements to
provide a reliable estimate of this quantity.  The results of this are shown in
the right panel of Figure~\ref{fig:lensstats}.  We consider two limiting
thresholds: $\mu_{\rm min} = 1.1$ and $\mu_{\rm min} = 2.0$.  The models we
consider are the same as those used in the left panel of
Figure~\ref{fig:lensstats}, and our method of creating the running average is
also the same.

>>>>

An excess of sources with small separations from each other could be an
indication of interacting or merging systems.  However, it is also possible
that the sources are merely unrelated galaxies that appear blended due to
projection effects \citep{HB13}.  Spatially resolved spectroscopy is necessary
to answer this question definitively, but is not currently available.  Instead,
to investigate these possibilities further, we make use of mock catalogs of
DSFGs that are based on numerical simulations and presented by \citet{HB13}.
We summarize the methodology used to generate $dN/dA$ values from the mock
catalogs here and refer the reader to \citet{HB13} for full details.

@@

We explore a variety of intrinsic luminosity functions that are described by
either a single Schechter function or a broken-power law.  These luminosity
functions are selected to represent the range of observed instrinsic luminosity
functions for DSFGs, which are shown in the left panel of
Figure~\ref{fig:lensstats} and are drawn from the ALESS survey
\citep{Karim:2013lr} and from interferometric follow-up of the first AzTEC
survey in COSMOS \citep{Scott:2008qy} using the SMA \citep{Younger:2007fk,
Younger:2009lr} and PdBI \citep{Miettinen:2015lr}.  Interferometric follow-up
data in COSMOS \citep{Smolcic:2012zl} and GOODS-N \citep{Barger:2012yg} are
published, but unknown completeness corrections in the single-dish surveys on
which these follow-up datasets are based precludes their use here.

@@

In Table~\ref{tab:models}, we provide information for two models tested in this
paper: the \citet{Karim:2013lr} broken power-law that provides a good fit to
ALESS number counts; and a broken power-law with a brighter break point
($S_\ast = 15\,$mJy) that provides a good fit to the COSMOS luminosity function
from \citet{Miettinen:2015lr}.  The data and corresponding luminosity functions
are shown in the left panel of Figure~\ref{fig:lensstats}.

@@

The middle panel of Figure~\ref{fig:lensstats} shows a direct comparison of the
measured $\mu_{870}$ values as a function of apparent $S_{870}$ for the {\it
Herschel}-ALMA and {\it Herschel}-SMA samples.  We also show a running average
of the combined sample (considering only $\mu_{870} > 2.0$ objects) to serve as
a direct comparison to our theoretical models.  We compute this by
interpolating the observed $\mu_{870}$ and $S_{870}$ onto a fine grid using the
{\sc Scipy} {\sc griddata} package and then smoothing the resulting grid using
a Gaussian filter in the Scipy {\sc gaussian\_filter} package.
Also shown in this diagram are model predictions for the average magnification
as a function of $S_{870}$, $\langle\mu_{870}\rangle$, assuming the two
intrinsic luminosity functions for DSFGs described in Table~\ref{tab:models}.

\begin{figure*}[!tbp] 
%\epsscale{1.00} 
\includegraphics[width=0.335\textwidth]{../Figures/DifferentialNumberCounts.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/s870_mu_z1p5.pdf}
\includegraphics[width=0.335\textwidth]{../Figures/Pmu_S870_z1p5.pdf}

\caption{ {\it Left}: Observed luminosity functions from interferometer
follow-up of mm sources in COSMOS \citep[black circles;][]{Younger:2007fk,
Younger:2009lr, Miettinen:2015lr} and from ALESS \citep[pink
diamonds;][]{Karim:2013lr}.  The magneta and blue lines represent the range of
plausible intrinsic luminosity functions for DSFGs given these two datasets.
{\it Middle}: Magnification factors at 870$\,\mu$m as a function of apparent
$S_{870}$ for every source in our ALMA (green squares) and SMA (red circles)
samples.  The black line represents a running average of the magnification
measurements when sources with $\mu_{870} > 2.0$ are considered (grey shaded
region highlights the 1$\sigma$ uncertainty), and is truncated at the minimum
flux density at which we have observed $\mu_{870} > 2.0$.  Colored lines show
the average magnification factor, $\langle\mu_{870}\rangle$, predicted by our
models for the two intrinsic luminosity functions shown on the left.  The model
luminosity functions predict higher $\langle\mu_{870}\rangle$ than are seen in
the data.  {\it Right}: Probability that a source with a given $S_{870}$
experiences $\mu_{870} > 2.0$.  The black line (grey shaded region) shows a
logistic regression fit to the SMA and ALMA data (grey shaded region highlights
the 1$\sigma$ uncertainty).  Colored lines are the same as in the middle and
left panels.  The intrinsic luminosity function that provides a good fit to the
COSMOS data predicts too many unlensed or weakly lensed sources with intrinsic
flux densities of $S_{870}^\prime \sim 50\,$mJy.} \label{fig:lensstats}

@@

%At low apparent flux densities ($S_{870} < 10\,$mJy), all three models are
%broadly consistent with each other, as well as with the running average of the
%data, considering the dispersion in the model predictions for $\mu_{870}$ at a
%given $S_{870}$ are $\sigma_\mu \approx 1-2$ in this regime.

%The regime between the low and high apparent flux density limits ($10\,$mJy$ <
%S_{870} < 70\,$mJy) is where the three model predictions show the largest
%difference in $\langle\mu_{870}\rangle$.  The steep rise in the running
%average in this area is best reproduced by the model with the steep broken
%power-law luminosity function.  
Both models predict higher $\langle\mu_{870}\rangle$ than are seen in the data
by factors of 5-10.  However, the dispersion in the predicted
$\langle\mu_{870}\rangle$ values for both intrinsic luminosity functions rises
smoothly from $\sigma_\mu \approx 2$ at $S_{870} = 15\,$mJy to $\sigma_\mu
\approx 8$ at $S_{870} = 100\,$mJy, so this difference is not statistically
significant.  Furthermore, there is reason to believe that the data may be
biased against high magnification factor measurements.  In both the {\it
Herschel}-ALMA and {\it Herschel}-SMA samples, the spatial resolution is
$\approx 0\farcs5$.  This is nearly always sufficient to resolve the images of
the lensed galaxy, but it is not always sufficient to resolve the images
themselves.  Therefore, it may be the case that the lens models over-predict
the intrinsic sizes of the lensed galaxies and hence under-predict the
magnification factors.  For example, the half-light sizes of unlensed DSFGs
have been found recently to be $\approx 0.8 \,$kpc \citep{Ikarashi:2014nr} and
$\approx1.2\,$kpc \citep{Simpson:2015ty}.  In contrast, we reported a median
half-light radius of $1.53\,$kpc in \citet{Bussmann:2013lr}.  Early lens models
from higher resolution data with ALMA suggest that magnification factors could
increase by a factor of $\approx 1.5$ \citep{Rybak:2015fk}.  Therefore, it is
plausible that both of the intrinsic luminosity functions tested here provide
statistically consistent fits to the data.

A related but distinct test of the intrinsic luminosity functions for DSFGs
comes from the probability of a given source experiencing a magnification above
some threshold value, $\mu_{\rm min}$.  Unlike the case with the average
magnification factor measurements, our ALMA and SMA data should provide a
reliable estimate of this quantity.  The results of this are shown in the right
panel of Figure~\ref{fig:lensstats}.  For clarity of presentation, we show one
choice of $\mu_{\rm min}$: $\mu_{\rm min} = 2.0$.  The shape of the curves
varies with  $\mu_{\rm min}$, but the overall results are qualitatively the
same.  The models we consider are the same as those used in the left panel of
Figure~\ref{fig:lensstats}.  Instead of computing a running average of the
data, we show a logistic regression fit to the data \citep[obtained with the
{\sc Scikit-learn package;][]{scikit-learn}.
